The Mitsubishi RV8-CRL robot an 8-axis industrial robotic system with 6 main joints and 2 additional axes has been chosen for this project. Its payload capacity of 8 kg makes it suitable for the task at hand. The goal is to program the robot to demonstrate how industrial robots are utilized in the automotive industry, specifically for painting various automotive and air vehicle parts.\\
Key features of the RV-8CRL robot include:
\begin{itemize}
    
\item Rotational Axes: The robot's rotational axes allow for precise motion and coordination during painting.
\item Versatility: With its 8-axis composition, the robot offers freedom and flexibility in its actions.
\item Trajectory Control: Each axis contributes to accurate task execution.
\item Safety Sensors: The robot is equipped with integrated inductive sensors along its linear rail. These sensors identify end points and enhance safety.
\item Emergency Stop Buttons: An additional sensor ensures protection by allowing the robot to halt its movements instantly to prevent injuries.
\item Programming Sequence: The RV-8CRL robot's programming involves a predefined sequence of stages for efficient paint spraying. It calibrates itself, moves its joints according to the program, and sprays when needed.
\item Linear Rail (7th Axis): The linear rail enables the robot to move precisely and perform the required tasks.

\end{itemize}
%The Mitsubishi RV-8CRL robot, an 8-6 joints with two additonal axes industrial robotic system with a payload capacity of 8 kg, has been selected for this project. The purpose is to program the robot to display a prototype of how an industrial robot is used in automotive industries where different automotive and air vehicle parts are painted, using its rotational axes for precise motion and coordination. The RV-8CRL robot exhibits an 8-axis composition, allowing much freedom and versatility in action. Each axis of trajectory is leveraged for careful to perfrom the task accurately. Integrated inductive sensors on linear rail identify the end poiunts of the rail. There is an additional sensor, e-stop buttons.These sensors are essential in ensuring protection by allowing the robot to halt its movements and avoid bodily injuries. The programming of the RV-8CRL robot involves developing a predefined sequence of stages for spraying the paint. The series includes motions like caliberating itself, then moving different joint as per the program and spraying when it is needed to be sprayed. The 7th - axis which is a linear rail enable the robot to move and perform the required task.